Analysis

### 2022-07-20 02_EDA_SCREEN.Rmd
More comments

```{r}
mtx_to_gr <- function(mtx = mtx_human, genome_id = "hg38") {
  gr <- GRanges(seqnames = mtx$X1, 
              IRanges(start = mtx$X2, 
                      end = mtx$X3))

@@

```{r}
hg38.SCREEN.GRCh38_CTCF <- mtx_to_gr(mtx = mtx_human, genome_id = "hg38")
length(hg38.SCREEN.GRCh38_CTCF)
summary(width(hg38.SCREEN.GRCh38_CTCF))
mm10.SCREEN.mm10_CTCF <- mtx_to_gr(mtx = mtx_mouse, genome_id = "mm10")
length(mm10.SCREEN.mm10_CTCF)
summary(width(mm10.SCREEN.mm10_CTCF))

>>>>

```{r}
# Function to convert SCREEN data to GRanges
mtx_to_gr <- function(mtx = mtx_human, genome_id = "hg38") {
  gr <- GRanges(seqnames = mtx$X1, 
              IRanges(start = mtx$X2, 
                      end = mtx$X3))

@@

```{r}
# Convert SCREEN data to GRanges
hg38.SCREEN.GRCh38_CTCF <- mtx_to_gr(mtx = mtx_human, genome_id = "hg38")
length(hg38.SCREEN.GRCh38_CTCF)
summary(width(hg38.SCREEN.GRCh38_CTCF))
mm10.SCREEN.mm10_CTCF <- mtx_to_gr(mtx = mtx_mouse, genome_id = "mm10")
length(mm10.SCREEN.mm10_CTCF)
summary(width(mm10.SCREEN.mm10_CTCF))

### 2022-07-20 03_EDA_CTCFBSDB.Rmd
More comments

```{r}
mtx_to_gr <- function(mtx = mtx_human, genome_id = "hg19") {
  gr <- GRanges(seqnames = sapply(mtx$`Chromosome Location`, function(x) strsplit(x, ":|-")[[1]][1]), 
              IRanges(start = sapply(mtx$`Chromosome Location`, function(x) strsplit(x, ":|-")[[1]][2]) %>% as.numeric(), 
                      end = sapply(mtx$`Chromosome Location`, function(x) strsplit(x, ":|-")[[1]][3]) %>% as.numeric()))

@@

hg18.CTCFBSDB.CTCF_predicted_human <- mtx_to_gr(mtx = mtx_human, genome_id = "hg18")
length(hg18.CTCFBSDB.CTCF_predicted_human)
summary(width(hg18.CTCFBSDB.CTCF_predicted_human))
mm8.CTCFBSDB.CTCF_predicted_mouse <- mtx_to_gr(mtx = mtx_mouse, genome_id = "mm8")
length(mm8.CTCFBSDB.CTCF_predicted_mouse)
summary(width(mm8.CTCFBSDB.CTCF_predicted_mouse))

@@

```{r}
# Function to download a chain for the gf18_to_XX conversion and create a GRanges object
liftOver_custom <- function(URL = "https://hgdownload.cse.ucsc.edu/goldenpath/hg18/liftOver/hg18ToHg19.over.chain.gz", gr_in = hg18.CTCFBSDB.CTCF_predicted_human, genome_id = "hg19"){
  fileChain <- file.path(dir_project, "data", basename(URL))
  if (!file.exists(str_remove(fileChain, ".gz"))) {
    download.file(URL, destfile = fileChain)
    R.utils::gunzip(fileChain)
  }

>>>>

```{r}
# Function to convert CTCFBSDB data to GRanges
mtx_to_gr <- function(mtx = mtx_human, genome_id = "hg19") {
  gr <- GRanges(seqnames = sapply(mtx$`Chromosome Location`, function(x) strsplit(x, ":|-")[[1]][1]), 
              IRanges(start = sapply(mtx$`Chromosome Location`, function(x) strsplit(x, ":|-")[[1]][2]) %>% as.numeric(), 
                      end = sapply(mtx$`Chromosome Location`, function(x) strsplit(x, ":|-")[[1]][3]) %>% as.numeric()))

@@

  return(gr)
}
# Convert CTCFBSDB data to GRanges
hg18.CTCFBSDB.CTCF_predicted_human <- mtx_to_gr(mtx = mtx_human, genome_id = "hg18")
length(hg18.CTCFBSDB.CTCF_predicted_human)
summary(width(hg18.CTCFBSDB.CTCF_predicted_human))
mm8.CTCFBSDB.CTCF_predicted_mouse <- mtx_to_gr(mtx = mtx_mouse, genome_id = "mm8")
length(mm8.CTCFBSDB.CTCF_predicted_mouse)
summary(width(mm8.CTCFBSDB.CTCF_predicted_mouse))

@@

```{r}
# Function to LiftOver hg18-hg19-hg38, mm8-mm9-mm10
# Downloads a chain for the gf18_to_XX conversion and create a GRanges object
liftOver_custom <- function(URL = "https://hgdownload.cse.ucsc.edu/goldenpath/hg18/liftOver/hg18ToHg19.over.chain.gz", gr_in = hg18.CTCFBSDB.CTCF_predicted_human, genome_id = "hg19"){
  fileChain <- file.path(dir_project, "data", basename(URL))
  if (!file.exists(str_remove(fileChain, ".gz"))) {
    download.file(URL, destfile = fileChain)
    R.utils::gunzip(fileChain)
  }
